\documentclass{book}

\usepackage{amsmath, amsthm, amssymb}
\usepackage{hyperref}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]

\title{SBS-Test: Formalization Status Report}
\author{Side-By-Side Blueprint Project}

\newcommand{\N}{\mathbb{N}}

\begin{document}

\chapter{Introduction}

This paper demonstrates the Side-by-Side Blueprint paper generation system.
We present a structured dependency graph with three branches that exercise
all six formalization status types. The integration of formal proofs with
traditional mathematical exposition enables direct verification of claimed results.

Our main contributions are:
\begin{enumerate}
\item A fully verified chain of propositional logic results (Branch C)
\item Demonstration of sorry propagation through arithmetic results (Branch A)
\item Integration of the Lean \texttt{axiom} keyword in set-theoretic results (Branch B)
\item A mathlib-ready theorem on the clean dependency chain
\end{enumerate}

\chapter{Foundations}

\section{Not Ready (Sandy Brown)}

A node is \emph{not ready} when it has not yet been prepared for formalization.
The foundation lemma is manually marked notReady, connecting the informal
base axiom to the formal development.

\paperstatement{foundation}

The full declaration with proof:

\paperfull{foundation}

\section{Ready (Light Sea Green)}

A node is \emph{ready} when the proof strategy is clear and formalization
can proceed. The natural number identity is marked ready, awaiting upstream work.

\paperstatement{nat_identity}

\chapter{Branch A: Arithmetic}

\section{Sorry (Dark Red)}

When a proof contains \texttt{sorry}, the node receives sorry status automatically.
This indicates that the formalization is incomplete.

\paperfull{add_zero}

The sorry propagates: even though add\_comm has a different statement,
it also contains sorry and blocks downstream verification.

\paperfull{add_comm}

\section{Proven with Sorry Ancestors}

Add\_assoc has a complete proof but cannot be fullyProven because
its ancestry includes sorry nodes.

\paperfull{add_assoc}

\chapter{Branch C: The Fully Proven Chain}

\section{Proven Leaf}

Our chain begins with a proven leaf node that has no dependencies.
Since all ancestors (vacuously) are proven, this node is auto-computed
as fullyProven.

\paperfull{proven_leaf}

\section{Transitivity of Implication}

\paperstatement{imp_trans}

\section{Weakening Principle}

\paperfull{weakening}

\section{Diamond Pattern}

The contrapositive and disjunction introduction demonstrate a diamond pattern
in the dependency graph.

\paperstatement{contrapositive}

\paperfull{disjunction_intro}

\chapter{Main Results}

\section{Core Theorem}

The core theorem merges Branches A and B in a diamond pattern,
with both add\_assoc and subset\_refl tracing back to foundation.

\paperfull{core_theorem}

\section{Main Result}

\paperstatement{main_result}

\section{Mathlib Ready (Light Blue)}

Nodes marked \emph{mathlib ready} are candidates for upstreaming to Mathlib.
This theorem depends only on the fully proven chain (Branch C).

\paperfull{mathlib_ready}

\end{document}
